---
title: "Assignment_9"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(MASS)
library(GGally)
library(modelr)
library(patchwork)
df <- read.csv("../../Data/GradSchool_Admissions.csv")

```

# Making a Summary and Cleaning the Data
```{r}


summary(df)

#clean data
df$admit <- as.logical(df$admit)

df$rank <- factor(df$rank)
```

# Testing some Models
```{r}

mod1 <- glm(data=df, formula = admit~ gre + rank * gpa)

mod2 <- glm(data= df, formula = admit~ rank + gpa+ gre, family = "binomial")

stepAIC(mod1)
stepAIC(mod2)

mean(mod2$residuals^2)
```
We will go with the second model.






Making a  new data frame with predictions
```{r}
df_pred <- add_predictions(df,mod2, type = "response")
```


# Showing various plots of the predicted data
```{r}
ggplot(df_pred, aes(x=gpa, y=pred)) + geom_point()
```



It appears that acceptance should go up with gpa, but lets include rank as well.



```{r}
ggplot(df_pred, aes(x=gpa, y=pred, color=rank)) + geom_point()

```



It looks like the higher rank undergraduate school you come from, the higher your expected acceptance.

Also within each rank, the higher gpa increases expected acceptance.


# Now lets look at gre predictions:
```{r}

ggplot(df_pred, aes(x=gre, y=pred, color=rank)) + geom_point()
```



We get very similar results, with higher gre increasing likelihood of graduate school acceptance. 

Note that higher ranked schools still having the advantage.


# Now lets compare predictions with reality:
```{r}
p1 <- ggplot(df, aes(x= gre, y= admit, color=rank)) +geom_point()
p2 <- ggplot(df_pred, aes(x=gre, y=pred, color=rank)) + geom_point()
p1 + p2

p3 <- ggplot(df_pred, aes(x=gpa, y=pred, color=rank)) + geom_point()
p4 <- ggplot(df, aes(x= gpa, y= admit, color=rank)) +geom_point()
p3 + p4

```

# Conclusion from the comparison:

These show us that while it is rare, individuals with low gre and/or gpa do in reality get admitted to grad school.

Does this mean our model and graphs are bad predictors? 

No, reality just has many more variables than we can account for. 
