---
title: "Exam 3 markdown"
author: "Dalton Hall"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(MASS)
library(patchwork)
library(modelr)
library(broom)
```
We start by loading the data used for our first task

```{r}
Fs1 <- read_csv("./FacultySalaries_1995.csv")
```
Then change some our data to long format for clarity

```{r}
fs2 <- pivot_longer(Fs1, cols = 5:7, names_to ="Rank", values_to = "Salary")

fs3 <- pivot_longer(fs2, cols = 6:8, names_to = "Comp", values_to= "Comp_value")

fs4 <- pivot_longer(fs3,cols = 7:10, names_to = "Employees", values_to= "Employee_value")
```


Removing erroneous data
```{r}
fs5 <-fs4[-c(41545:41580), ]
```
You could also do something like, fs_filtered <- filter(fs4, Tier == "I" | Tier == "IIA" | Tier == "IIB")


Plotting Data
```{r}
ggplot(fs5, aes(x=Rank, y=Salary, fill=Rank)) + geom_boxplot()+ facet_wrap(~Tier)+ theme_minimal()+ theme(axis.text.x = element_text(angle = 60, hjust=1))

```


Save plot as jpeg file
```{r}
ggsave(filename = "HALL_Fig_1.jpeg")    
```


# Task 2



Creating anova table
```{r}
anova_table<- aov(Salary ~ State + Tier + Rank, data =fs5)

anova_summary <- summary(anova_table)

anova_summary


```


Turning anova table into a txt file
```{r}
capture.output(anova_summary, file = "./Salary_ANOVA_Summary.txt")


```


Load next data set

```{r}
jo1<- read_csv("./Juniper_Oils.csv")

```


# Task 3- Cleaning the loaded data
```{r}
jo2<-pivot_longer(jo1,cols= 11:33, names_to="Chemicals", values_to= "Concentration")

```


## Task 4-Plotting the cleaned data, then saving the image

```{r}
ggplot(data=jo2,aes(x=YearsSinceBurn, y=Concentration))+theme_minimal()+facet_wrap(~Chemicals, scales = "free")+geom_smooth()
p2 <-ggplot(data=jo2,aes(x=YearsSinceBurn, y=Concentration))+theme_minimal()+facet_wrap(~Chemicals, scales = "free")+geom_smooth()

ggsave(filename = "HALL_Fig_2.jpeg",p2) 
```


# Task 5 

Make a linear model to show significant chemical concentrations against years since burn
```{r}
glm(data=jo2, formula = Concentration~YearsSinceBurn+ Chemicals)

jmod <- glm(data=jo2, formula = Concentration~YearsSinceBurn+ Chemicals)

```


Use tidy to create data frame with just significant chemicals
```{r}
options(scipen = 999)

tidy(jmod)

tidytable <- tidy(jmod)

sigs_chems <- filter(tidytable, p.value < 0.05)
```


Clean names of chemicals in the frame
```{r}
sigs_chems$term <- gsub("Chemicals","",sigs_chems$term)

print(sigs_chems)
```

